Will Kamala Harris will win the 2024 Presidential election

### 2024-11-04 paper/paper.qmd
llm added

Now, if we look at @fig-supportGNN Harris had a spike in early September like many other states where she was polling around 48%, but afterwards had a minor but gradual decline 
since. Although when we take a look at our model results in @fig-modelGANM we see that our prediction is that Harris's support is predicted to increase in North Carolina.

North Carolina is a significantly difficult state to predict when we consider its Republican history, predicted support for Harris, and @fig-supportstate, where both candidates are neck and neck the chance for this state to go to either candidate is very up in the air.

We believe North Carolina will vote: **Donald Trump**

>>>>

Now, if we look at @fig-supportGNN Harris had a spike in early September like many other states where she was polling around 48%, but afterwards had a minor but gradual decline 
since. Although when we take a look at our model results in @
